Debugging by \textit{lastChange}

### 2010-10-26 trunk/papers/pldi2011/sigplanconf-template.tex

%---------------------------------------------------------------------------------------------------
\section{Introduction}
Debugging is an inevitable part of programming, still hard and time-consuming. To fix a bug, developers have to reproduce and monitor the buggy execution several times to understand the program's unexpected behavior. Trial and error, guess-work and analyzing huge collected data are the inseparable parts of this process. According to \cite{LaToza}, developers spend about fifty percent of their time debugging. Therefore, enhancements to debugging techniques and tools can considerably save developers' time and improve programs' quality.

@@

%---------------------------------------------------------------------------------------------------
\section{Introductory example}

@@

%---------------------------------------------------------------------------------------------------
\section{\textit{lastChange} Algorithm}

@@

The Firefox JavaScript engine does not current support
\texttt{setPropertyChangeHook()} (see however []).  For %\cite{bugzilla}
the our \textit{lastChange} prototype we created a version of
\texttt{setPropertyChangeHook()} using only features of the current
engine.  The basic strategy is to get a reference to the object just
after its creation, then use \texttt{watch()} function to monitor
property changes in the object.  Setting a flag into the Firefox
JavaScript engine we can get file URL and line number for each object
creation (e.g., myFile.js, line 24). We set a hook on this line
and analyze the source code to determine which object was created.

@@

An object might be created by one of these statements: An object
initializer (\texttt{\{...\}}), \textit{new} operator (\texttt{new 
constructor()}) or function definition statment (\texttt{function()}). 
By parsing the source code we can easily recognize the statements 
create an object. The next step is getting a reference to the new object.

@@

%The algorithm is not complete and it is tried to support more and more cases

\subsection{\texttt{scopeId()} operation}
Debugger sets a hook at the beginning of all code blocks need
a scope id whenever the block is loaded. The scope id is kept as a variable with name 
\texttt{\_scopeId} in the scope. Whenever the hook hits which means a new scope
is created, \texttt{\_scopeId} is set by calling JavaScript's dynamic compilation 
function \texttt{eval()}. For example, executing \texttt{eval( var \_scopeId = 10)} creates a
variable with name \texttt{\_scopeId} and value \texttt{10} in the
scope of the \texttt{eval()} call, which is our interesting scope.

@@

%---------------------------------------------------------------------------------------------------
\subsection{Execution reproduction}
Although execution reproduction is basicly should be provided by the
developer, we tried to devise some automatic way which reproduces the
execution. In \textit{Querypointer}, develooper can directly provide a
test case which reproduces the execution. It is also possible to use
two automatic reproduction option: record-replay or local-reproduction
.

@@

\subsection{Data collection and presentation}
So far, we talked about the data collected at change events for
\textit{lastChange} algorithm. However, if developer needs to explore
the program state at a given point, more data is required. It is
possible to postpone data collection until user requests. It is also
possible to collect the list of available
variable. \textit{Querypointer} collects data in one level depth. More
data will be collected upon the developer's request by re-execution.

@@

>>>>

\section{Introduction}
Debugging is an inevitable part of programming, still hard and time-consuming. To fix a bug, developers have to reproduce and monitor the buggy execution several times to understand the program's unexpected behavior. Trial and error, guess-work and analyzing huge collected data are the inseparable parts of this process. According to \cite{LaToza}, developers spend about fifty percent of their time debugging. Therefore, enhancements to debugging techniques and tools can considerably save developers' time and improve programs' quality.

@@

\section{Introductory example}

@@

\section{\textit{lastChange} Algorithm}

@@

The Firefox JavaScript engine does not current support
\texttt{setPro-}
\texttt{pertyChangeHook()} (see however []).  For %\cite{bugzilla}
the our \textit{lastChange} prototype we created a version of
\texttt{setPropertyChangeHook()} using only features of the current
engine.  The basic strategy is to get a reference to the object just
after its creation, then use \texttt{watch()} function to monitor
property changes in the object.  Setting a flag into the Firefox
JavaScript engine we can get file URL and line number for each object
creation (e.g., myFile.js, line 24). We set a hook on this line
and analyze the source code to determine which object was created.

@@

An object might be created by one of these statements: object
initializer (\texttt{\{...\}}), \textit{new} operator (\texttt{new 
constructor()}) or function definition statment (\texttt{function()}). 
By parsing the source code we can easily recognize the statements 
create an object. The next step is getting a reference to the new object.

@@

\subsection{\texttt{scopeId()} operation}
Debugger sets a hook at the beginning of all code blocks need
a scope id whenever the block is loaded. The scope id is kept as a variable with name 
\texttt{\_scopeId} in the scope. Whenever the hook hits which means a new scope
is created, \texttt{\_scopeId} is set by calling JavaScript's dynamic compilation 
function \texttt{eval()}. For example, executing \texttt{eval( var \_scopeId = 10)} creates a
variable with name \texttt{\_scopeId} and value \texttt{10} in the
scope of the \texttt{eval()} call, which is our interesting scope. \texttt{scopeId()}
operation returns the value of \texttt{\_scopeId} in the scope.

@@

\subsection{Execution reproduction}
Although execution reproduction is basicly should be provided by the
developer, we tried to devise some automatic way which reproduces the
execution. In \textit{Querypointer}, develooper can directly provide a
test case which reproduces the execution. It is also possible to use
two automatic reproduction option: record-replay or local-reproduction.

@@

\subsection{Data collection}
So far, we talked about the data collected at change events for
\textit{lastChange} algorithm. However, if developer needs to explore
the program state at a given point, more data is required. It is
possible to postpone data collection until user requests. It is also
possible to collect the list of available
variable. \textit{Querypointer} collects data in one level depth. More
data will be collected upon the developer's request by re-execution.

@@

% Discuss what happens when assumptions changes, like object creation location.
